The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-06-25 Paper.Rmd

csl: ecology-letters.csl
bibliography: REF_ALL.bib
---
updated on `r Sys.Date()`
```{r setup_Paper, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
#seed<-101
#source("mtime.R") #A function needed for caching
```
# Front matter

@@

The model-averaged (AIC weights used for model averaging) lower-tail dependence statistic was <!--$\num{1e-10}$--> `r round(BivMS_contrasts_67$relLTdep_AICw,3)` <!--`r BivMS_contrasts_67$relLTdep_AICw` this is e-4 could not compile latex--> and the model-averaged upper-tail dependence statistic was `r BivMS_contrasts_67$relUTdep_AICw`. These values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper), `r BivMS_contrasts_67$relLTdep_AICw-BivMS_contrasts_67$relUTdep_AICw`, was different from 0, answering the third part of question 1.

>>>>

csl: ecology-letters.csl
bibliography: REF_ALL.bib
---
updated on `r Sys.Date()`
```{r setup_Paper, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
options(scipen = 1, digits = 5) #This option round all numbers appeared in the inline r code upto 5th digit
#seed<-101
#source("mtime.R") #A function needed for caching
```
# Front matter

@@

The model-averaged (AIC weights used for model averaging) lower-tail dependence statistic was `r BivMS_contrasts_67$relLTdep_AICw` and the model-averaged upper-tail dependence statistic was `r BivMS_contrasts_67$relUTdep_AICw`. These values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper), `r BivMS_contrasts_67$relLTdep_AICw-BivMS_contrasts_67$relUTdep_AICw`, was different from 0, answering the third part of question 1.
